Curation of NYC 311 Request Open Data

### 2023-06-09 talk/slides.Rmd

## NYC 311 Open Data

- Open Data is viewed as a right for all.
- Cities lead open data efforts wtih >50 cities with formal programs.
- NYC is a forerunner with Open Data Law in 2012.
- Today NYC Open Data has 3511 datasets from 98 Agencies, accesible online.
- 311 Service Request data is the most viewed dataset at NYC Open Data.
- Used in STAT 3255/5255 Introduction to Data Science at UConn
- Exported 1-31 March 2023 311 SRs for analysis (~250K records).

>>>>

## NYC Open Data

- Open Data is viewed as a right for all [@janssen2012benefits; @wang2016adoption].
- Cities lead open data efforts wtih >50 cities with formal programs.
- NYC is a forerunner with Open Data Law in 2012 [@zuiderwijk2014open].
- Today NYC Open Data has 3511 datasets from 98 Agencies, accesible online.
- Used in many research
    + Health [@cantor2018facets, shankar2021data]
    + Smart city [@neves2020impacts]
    + Transportation [@gerte2019understanding]

## NYC 311 Service Requests

- 311 Service Request data is the most viewed dataset at NYC Open Data.
- Used in STAT 3255/5255 Introduction to Data Science at UConn
- In this study, we exported 1-31 March 2023 311 SRs for analysis (~251K records).
- Data curation is imporant issue for open data such as the 311 SRs [@witt2009constructing; @borgman2012conundrum; @mclure2014data; @barns2016mine; @hart2016ten; @beheshti2019datasynapse; @shankar2021data].
